---
title: "Problem 2: Polty"
output: 
  html_document:
    toc: true
    toc_float: true
---

## Load the Package
```{r}
library(tidyverse)
library(p8105.datasets)
library(plotly)
```

I select NYC Restaurant Inspections to make the plot.

## Load and clean the dataset 
```{r}
data("rest_inspec")

rest_inspec <- 
  rest_inspec %>% 
  rename("borough" = "boro") %>%
  select(dba, borough, cuisine_description, critical_flag, 
         score, grade, inspection_date) %>%
  separate(inspection_date, into = c("year", "month", "day"), sep = "-") %>% 
  filter(borough == "QUEENS",
         critical_flag == "Critical",
         grade == "C") %>% 
  drop_na() %>% 
  distinct() 

```

I selected restaurant from Queens, Critical_flag = "Critical" that most likely contribute foodborne illness, and lowest grade("C"). There were total `r nrow(rest_inspec)` of unique restaurants after filtering. The important varaibles were score, cuisine_description, year.


## 1. Bar plot 
```{r}
rest_inspec %>% 
  count(cuisine_description) %>% 
  mutate(cuisine_description = fct_reorder(cuisine_description, n)) %>% 
  plot_ly(x = ~cuisine_description, y = ~n, type = "bar") 
```

From the bar plot, Chinese cuisine has the most number of critical flag among grade C restaurants in Queens.

## 2. Line plot
```{r}
rest_inspec %>% 
  count(year) %>% 
  plot_ly(x = ~year, y = ~n, type = "scatter", mode = "lines")
```

for number of grade C restaurant that has critical flag in Queens, the line plot show a increasing trend from 2013 to 2015 and a decreasing trend from 2015 to 2017. 

## 3. boxplot

```{r}
rest_inspec %>%
  mutate(cuisine_description = fct_reorder(cuisine_description, score)) %>% 
  plot_ly(y = ~score, color = ~cuisine_description, type = "box", colors = "viridis")
```

Paklstanl cusine has the lowest score in the inspection, Turkish cuisine has the highest score in the inspection. 

